% !TEX encoding = UTF-8 Unicode

%\documentclass[a4paper,10pt]{report}
\documentclass[a4paper,10pt,twocolumn]{report}
\usepackage[natbibapa,nosectionbib,tocbib,numberedbib]{apacite}
\AtBeginDocument{\renewcommand{\bibname}{literature}}
\usepackage{color,soul}

\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{url}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage{pifont}

\usepackage{lmodern}
\usepackage{listings}
\lstset{
	basicstyle=\scriptsize\ttfamily,
	columns=flexible,
	breaklines=true,
	numbers=left,
	%stepsize=1,
	numberstyle=\tiny,
	backgroundcolor=\color[rgb]{0.85,0.90,1}
}


\let\oldquote\quote
\let\endoldquote\endquote
\renewenvironment{quote}{\footnotesize\oldquote}{\endoldquote}



\title{Computational Communication Science 2\\ Course Manual}
\author{dr. Anne Kroon (a.c.kroon@uva.nl)\\dr. Marthe Möller (a.m.moller@uva.nl) \\~\\College of Communication\\University of Amsterdam}
\date{Spring Semester 2022 (block 2)}


\begin{document}
	\maketitle
	
	\tableofcontents

	
	\chapter{About this course}
	
	This course manual contains general information, guidelines, rules and schedules for the course Computational Communication Science 2 (6 ECTs), part of the Communication in the Digital Society Minor offered by the College of Communication at the University of Amsterdam. Please make sure you read it carefully, as it  contains information regarding assignments, deadlines and grading.
	
	\section{Course description}
	
	A sales website that recommends new products to you personally, a company that uses a chatbot to answer your questions, or an algorithm that automatically identifies and warns you about fake news content: In our digital society, we use computational methods to communicate with each other every day. In this course, we will zoom in on the computational methods that lay behind these new ways of communication. We will explore the basic principles of their design, acquire an understanding of their implications, and learn how these methods can be used for science. We will work with some of these methods ourselves in the weekly lab sessions to get hands-on experience with these techniques and experience their advantages and limitations first hand. During weekly lectures, we will critically discuss the role that these methods play in our daily lives and what responsibility we have when working with them. At the end of the course, you will have a basic understanding of the methods that underlie different ways of communication in the digital society, you can formulate an informed opinion about the implications of these new techniques, and you will have some first-hand experience in working with them.
	
	In this 7-week course, each week consists of one lecture that zooms in on a specific computational method and the possible applications of this method and of one tutorial in which we work with this method. Through this mixture of introductions to computational methods in the lectures and a hands-on approach during the lab sessions, you will acquire knowledge on computational communication science that continues on the knowledge that you gained in CCS-2. In total, there are 28 contact hours in this course (7x 2-hour lecture and 7x 2-hour tutorial). 
	
	\section{Goals}
	Upon completion of this course, students should:
	\begin{enumerate}[a]
		\item Have a general understanding of state-of-the-art computational techniques useful to study communication phenomena in the digital society.
		\item Have a basic understanding of how to apply rule-based, unsupervised and supervised techniques to answer research questions in the field of communication science.
		\item Be able to identify key benefits and drawbacks associated with different rule-based and machine learning techniques.
		\item Have basic knowledge of what communication scientific questions can be answered using computational methods.
		\item Be able to apply a subset of these techniques independently in order to answer some basic research questions in the field of communication in the digital society.
		\item Have experience with independently solving problems in Python scripts by gathering information from online platforms.
		\item Be able to clearly communicate through written texts what steps were taken in a research project using computational methods.
	\end{enumerate}

	\section{Study materials}
	During this course, Python is the programming language that we will be working with. Hence, students should bring a laptop to each class, with a working Python environment installed.  
	
	In addition, a list of assigned readings is made available on the course Canvas page. All readings are available for download online using the UvA Digital Library or Google Scholar. If a reading is not available online, the material will be made available on the course Canvas page.
	
	
\chapter{Assignments, grading, and rules}
Assessment for this course is based on a mixture of individual and group assignments. 
	
	\section{Overview of assessments}
	The overall course grade is based on the following assignments:
	\begin{itemize}
		\item Regular multiple-choice questions (\(20\%\))
		\item Group assignment: Written report (\(20\%\))
		\item Group assignment: Presentation (\(10\%\))
		\item Take-home exam (\(50\%\))
	\end{itemize}

\section{Regular multiple-choice questions ($20\%$)}
At the start of the lab sessions, students will be asked to answer four questions about that week's literature and/or the preceeding lecture as well as about the content discussed in that week's lecture. All lab sessions will start with MC-questions, except for week 3 (19/04). This means that there are six weeks with MC-questions. In total, students can answer 24 questions (6 weeks * 4 questions). To receive full marks for this assignment, 18 questions need to be answered correctly. Hence, even if one of the lab sessions during which the MC-questions need to be answered is missed, it is still possible to receive full marks on the assignment. 
	
	\section{Group assignment: report ($20\%$)}
In groups of 4 students, you will work on a group assignment. See the description here in Section ~\ref{sec:groupassignment}
	
	\section{Group assignment: presentation ($10\%$)}
In week 7, you will present your group assignment in class. 
	
	\section{Take-home exam ($50\%$)}
	After the last lab session of the course (i.e., Tuesday, 24 May, 5 pm), students will receive a take-home exam. This exam will test students' understanding of concepts as discussed in the course. In addition, students are presented with a computational coding challenge on one of the techniques discussed in the course. The take-home exam is an open-book exam. Furthermore, it is an individual assignment that students make at home using their own computer. 

	\section{Grading}
	Students have to get a pass (5.5 or higher) for (1) the average of the group report and presentation, and (2) for the take-home exam. If the average grade of the group assignments or of the take-home exam is lower than 5.5, an improved version of the written work can be handed in within one week after the grade is communicated to the student(s). If the improved version still is graded lower than 5.5, the course cannot be completed. Improved versions of the group assignment and the take-home exam cannot be graded higher than 6.0. 
	
	\section{Deadlines and submitting assignments}
	Please send all assignments and papers as a PDF file to ensure that it can be read and is displayed the same way on any device. Hardcopies are not required. Multiple files should be compressed and handed in as one .zip file or .tar.gz file. Anything exceeding a reasonable file size (approximately 5 MB) has to be send via \url{https://filesender.surf.nl/} instead of direct email. Ensure that for all the files and/or folders you submit, your name(s) are included in the file-/ foldername. \\
	
	Assignments that are not completed on time, will be not be graded and receive the grade 1. 
		\begin{itemize}
			\item For the group report and the take-home exam, this means that all required files need to be submitted before the deadline. 
			\item The group presentation needs to held during the assigned class, meaning that slides or any other material used for the presentation needs to be present in class as well as at least one group member to give the presentation. 
		\end{itemize}
	Note that the deadline of an assignment is only met when the all files are submitted \emph{before} the deadline.

	\section{Plagiarism \& fraud}
	The provisions of the regulations governing fraud and plagiarism for UvA students apply in full to students of this course. The program Ouriginal will be used for the detection of plagiarism in written assignments. In submitting a text, the student consents to the text being entered in the database of the detection program concerned. Any suspicion of fraud and plagiarism (including self\‐plagiarism) will be reported to the Examinations Board. To avoid doing prohibited things ‘by accident’ or ‘due to ignorance’, we urgently advise you to consult the following site about \textbf{fraud and plagiarism}: https://student.uva.nl/en/content/az/plagiarism-and-fraud/plagiarism-and-fraud.html
	
		\subsection{Attributing code}
		Plagiarism rules apply to code as well. It is understandable that your code is inspired by the code on the slides of the lectures, and by solutions found on sources such as \texttt{stackoverflow}. That is how coding works; you build on the insights and solutions of others. While it is perfectly fine to rely on solutions provided by others, it is \emph{highly important} that you are transparant with respect to \emph{where you got your code from}. More specifically, it should be clear what is your own code, and which parts are derived from other sources. That is, if you copy-paste code and use it in your group assignment or take-home exam, please include a reference to it's source (by simply including a comment like: \texttt{# The following function is copied from https://stackoverflow.com/XXXXX/XXXXX} for (almost) literal copy-pasting, or \texttt{\# The code in this cell is inspired by https://...; I modified Y and Z}. 
	
	\section{Presence and participation}
	Attendance and active participation in the lectures and lab sessions are preconditions for obtaining the final grade. Students are expected to read the literature, to prepare and submit the assignments on time, and to actively participate in the discussions and exercises. \\

	Nonattendance is only allowed with a valid reason that is communicated to the lecturer before the meeting. If the student cannot attend a meeting, an email must be sent to the lecturer before the start of the session. Students are not allowed to miss more than two lectures or more than two lab sessions. When missing a meeting, students are still expected to submit all assignments on time. Students that skip more than two lectures or more than two lab sessions will not be able to complete the course. \\
	
	As you will have noticed in Computational Communication Science 1 and/or similar courses on coding, developing your skills to work with computational methods requires you to practice regularly and to be proactive when it comes to solving problems in your code. Hence, students of Computational Communication Science 2 are expected to practice with and revise the materials discussed in class at home. By practicing at home regularly in between classes, you will get the most out of this course and you will acquire the skills that you need to continue developing your programming knowledge after you finished this course. \\

	\underline{Class Lateness Policy:} Students are expected to arrive at class \underline{on time}. Being late twice will be considered as one nonattendance. \\

	\underline{Covid-19 Modifications:} Although this primary attendance policy stands, due to the Covid19 pandemic, any student with Covid or Covid-related symptoms must stay at home and take a test with the GGD.  Similarly, students are expected to follow all government guidelines related to quarantine. In these situations, students are permitted to livestream the lecture using the Zoom link established for the course. This livestream is considered attendance. \underline{Students must inform the teacher in advance} if they will be livestreaming the class. \\  

	\textbf{Note} that doctor's appointments, travel plans, bad weather, or other similar reasons are not sufficient reasons to follow the livestream – this attendance policy is specifically related to Covid. \underline{A maximum of three livestream sessions is allowed.} We also recommend that you find a buddy that can ask questions on your behalf during the session (livestream does not facilitate this well) and who can share any information you might miss.  If students must quarantine longer or are symptomatic longer than 3 livestreamed sessions, students must contact the study advisor. The study advisor can evaluate the situation and, as necessary, be in contact with the lecturer of the course or the Exam Committee depending upon the situation to discuss appropriate measures. 

	\section{Livestreaming of lectures and lab sessions}
	All meetings will be held in English. The assignments must be written and presented in English. 


	\section{Language}
	The livestreaming of lectures and lab sessions is \textbf{only} intended for students that have covid-19 symptoms or have to quarantine at home. 

	\section{Study advisors}
	The Study Advisers from Communication Science (https://student.uva.nl/communication-science/contact/study-advisers/study-advisers-cs.htm) are the go-to persons for all planning related questions concerning the Minor’s program and should be the ones contacted when indicated by the lecturers or by the course policies. They may refer you to the Study Advisers from your own course (if you do not follow the Communication Science Bachelor’s programme) when needed. 
	
	\section{Staying informed}
	It is your responsibility to check the means of communications used for this course (i.e., your email account, the course Canvas page, and the course Github page) on a regular basis, which in most cases means daily. 
	

	\chapter{Group Assignment}
	\label{sec:groupassignment}
	\input{GroupAssignment}
	
	
	\chapter{Course Schedule}
	
	\input{CourseSchedule}
	
	\bibliographystyle{apacite}
	\bibliography{../literature.bib}
	
	
	
\end{document}